\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-02 arch.tex
Further development in intertwined synch & planning

\subsubsection{Intertwining synchronization and execution }
\label{sec:arch:intertwine}

>>>>

\subsubsection{Intertwining synchronization and execution}
\label{sec:arch:intertwine}

A core aspect of this reactor is that it takes advantage of the
specific sequencing enforced by the T-REX architecture along with the
fact that only one $plan$ structure is maintained in the reactor and
shared between synchronization and planning to allow these two processes
to not only be interleaved but impact each other through the way they
manipulate this plan.

The most obvious case is how synchronization allow propagate of {\em
  external} observations as a new tick occur in the plan. In or
presentation of synchronization, we isolated the problem by stating
that we will assume at this point that the reactorhas no future goal
or more accurateely no plan to enforce at this stage. By doing so we
were able to develop the way we augment yhe europpa solver to be able
to propagete {\em external} observations in order to identify the
reactor {\em internal} state for the same tick. By doing so we were
able to focus on synchronization as a state evluation process that can
be resolved within the europa framework with few extensions. simliarly
we presented deliberation at this fairly high level not necessarily
discussing how the disruptive nature of synchronization in this
process could impact the way this planning process will evolve.

We first anlyse the case during which synchronization occurs after the
planning has vcompleted (ie the last seep of deliberation resulted into
a plan that is considered as complete for the current look-ahead). As
synchronization starts with  the plan produced this will gave a frame
for the search process. Therefore this deliberation will not only be a
model-based estimation uniquely based on the {\em external}
observations but will also include the reactor intentions as described
by the plan produced.
